Topological Equivariant Artist Model

### 2021-12-31 slides/main.tex
presheaf + functor

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

        }

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:1>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:1>{\arrow[d, "F(f)", shift right=0, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:9->{\dfiberc}
        \onslide*<9-|handout:9->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:3,6->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:4-5>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc} 
            \&  
            {} \& 
            \onslide*<6-|handout:6->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:7->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:3>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:4-5>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:6->{\opensetc_1} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<7-|handout:7->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:8->{\arrow[uu, "\sheafc_{\dbasec}" description, color=sheaf]} \& 
            \onslide*<6-|handout:6->{\opensetc_2} 
            \onslide*<6-|handout:6->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:9->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:10>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

>>>>

\begin{frame}{$\mathcal{C}^{op}$}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:1>{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}
        }

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:1>[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:1>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}
